Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-05-01 paper/paper7/paper7.tex
appendix

\section{Classification of Constraint Types and Constraints}
\label{classification}

Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We classified both RDF constraint types and RDF constraints to gain better insights into the quality of RDF data with respect to this classification, independent of the used vocabulary.
%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.

@@

We validated 
9,990 / 3,775,983,610 (\emph{QB}),
4,178 / 477,737,281 (\emph{SKOS}), and 
1,526 / 9,673,055 (\emph{Disco}) data sets / triples using our validation environment in batch mode.
We validated, i.a., 
(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
the \emph{European Central Bank}, and the
\emph{Organisation for Economic Co-operation and Development},
(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences}, and
(3) \emph{Disco} data sets provided by the \emph{Microdata Information System}, 
the \emph{Data Without Boundaries Discovery Portal}, the
\emph{Danish Data Archive}, and the
\emph{Swedish National Data Service}.
We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
in which we describe the evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.

@@

We identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
 of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.

For 114 of these constraints, we evaluated\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
 the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies.
The main hypotheses are: 
(1) The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
(2) The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
(3) 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
(4) As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}.

>>>>

\section{Classification of Constraint Types and Constraints}
\label{classification}
\tb{82 constraint types / 76 requirements}
Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as first appendix of this paper) in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We classified both RDF constraint types and RDF constraints to gain better insights into the quality of RDF data with respect to this classification, independent of the used vocabulary.
%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as second appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.

@@

We validated 
9,990 / 3,775,983,610 (\emph{QB}),
4,178 / 477,737,281 (\emph{SKOS}), and 
1,526 / 9,673,055 (\emph{Disco}) data sets / triples using our validation environment in batch mode.
We validated, i.a., 
(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
the \emph{European Central Bank}, and the
\emph{Organisation for Economic Co-operation and Development},
(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences}, and
(3) \emph{Disco} data sets provided by the \emph{Microdata Information System}, 
the \emph{Data Without Boundaries Discovery Portal}, the
\emph{Danish Data Archive}, and the
\emph{Swedish National Data Service}.
We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as third appendix of this paper) 
in which we describe the evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.

@@

We identified and published by today 82 types of constraints\footnote{The first appendix of this paper, in which we explain each requirement/constraint type in detail, is available at: \url{http://arxiv.org/abs/1501.03933} \cite{BoschNolleAcarEckert2015}}
that are required by various stakeholders for data applications.
In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
 of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.

For 114 of these constraints, we evaluated\footnote{The third appendix of this paper, in which we describe the evaluation in detail, is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
 the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies.
The main hypotheses are: 
(1) The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
(2) The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
(3) 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
(4) As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}.
